HO unification from object language to meta language

### 2024-03-22 paper/main.tex
update beta

The second circumstance making the \linkbeta to progress is the instantiation 
of the variables in the \elpiIn{Extra}.

and some of the arguments in the \elpiIn{NPF} list become names. This is
possible after the resolution of other links. In this case, the list \elpiIn{L}
obtained by the concatenation between \elpiIn{PF} and \elpiIn{NPF} is split
again in to lists \elpiIn{PF'} and \elpiIn{NPF'}. If \elpiIn{PF} is not that
same as \elpiIn{PF'}, then we can 1) remove the current \linkbeta, 2) create a
new \linkbeta between \elpiIn{T} and \elpiIn{app[uva N' PF' | NPF']} and 3)
create a new \linketa between the variables \elpiIn{N} and \elpiIn{N'}.

>>>>

The second circumstance making the \linkbeta to progress is the instantiation of
the variables in the \elpiIn{Extra1} making the corresponding arguments to
reduce to names. In this case, we want to take the list \elpiIn{Scope1} and
append to it the largest prefix of \elpiIn{Extra1} in a new variable
\elpiIn{Scope2} such that \elpiIn{Scope2} remains in \llambda; we call
\elpiIn{Extra2} the suffix of \elpiIn{Extra1} such that the concatenation of
\elpiIn{Scope1} and \elpiIn{Extra1} is the same as the concatenation of
\elpiIn{Scope2} and \elpiIn{Extra2}.

% and some of the arguments in the \elpiIn{NPF} list become names. This is
% possible after the resolution of other links. In this case, the list \elpiIn{L}
% obtained by the concatenation between \elpiIn{PF} and \elpiIn{NPF} is split
% again in to lists \elpiIn{PF'} and \elpiIn{NPF'}. If \elpiIn{PF} is not that
% same as \elpiIn{PF'}, then we can 1) remove the current \linkbeta, 2) create a
% new \linkbeta between \elpiIn{T} and \elpiIn{app[uva N' PF' | NPF']} and 3)
% create a new \linketa between the variables \elpiIn{N} and \elpiIn{N'}.
